---
title: "Homework 2: Stacked Model"
author: "Tom Davis and Jeremy Zhou"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    theme: spacelab
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Initial Data Setup

## Downloading and Prepping the Data

```{r}
#Downloading and Prepping the Data
tele <- read.csv("tele.csv", stringsAsFactors = TRUE)

#We are deleting the "duration" variable because it is an after the fact measurement. We only should be using variables that we know before the call
tele$duration <- NULL

# Deleting the column X
tele$X <- NULL

# Changing pdays to a dummy and deleting pdays
tele$pdaysdummy <- ifelse(tele$pdays == 999, 0, 1)
tele$pdays <- NULL

summary(tele)
```

## Getting Data Ready for Analysis

```{r}
# Using model.matrix to convert all the factors to dummy variables
# We are converting all of the factors into dummy variables as the input into knn has to be numeric

telemm <- as.data.frame(model.matrix(~.-1,tele))

# Randomize the rows in the data (shuffling the rows)
set.seed(12345)
tele_random <- telemm[sample(nrow(telemm)),]

#Normalize the data
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}

# we are going to normalize everything 
tele_norm <- as.data.frame(lapply(tele_random, normalize))
```


## Getting Train and Test Samples

```{r}
# Selects 10000 random rows for test data
set.seed(12345)
test_set <- sample(1:nrow(tele_norm), 0.5*nrow(tele_norm)) 
# Depending on R-version and computer, different rows may be selected. 
# If that happens, results are different. 

# Create a train set and test set
#First the predictors - all columns except the yyes column
tele_train <- tele_norm[-test_set, -match("yyes",names(tele_norm))]
tele_test <- tele_norm[test_set, -match("yyes",names(tele_norm))]

#Now the response (aka Labels) - only the yyes column
tele_train_labels <- tele_norm[-test_set, "yyes"]
tele_test_labels <- tele_norm[test_set, "yyes"]

#Creating Full Training and Testing Datasets
tele_test_full <- tele_norm[test_set, ]
tele_train_full <- tele_norm[-test_set, ]

```


# Building Our Models

## Logistic Regression Model Creation
```{r}
LogModel <- lm(yyes ~ ., data = tele_train_full)
```

## Logistic Model Testing
```{r}
library(caret)
LogPred <- predict(LogModel, tele_test_full)
predbin_log <- ifelse(LogPred >= 0.5, 1, 0)
confusionMatrix(as.factor(predbin_log), as.factor(tele_test_full$yyes), positive = "1")

#Kappa for this model = 0.2826
```

## KNN Model Creation
```{r, cache=TRUE}
library(class)

#Output is the prediction for the testing dataset
KNNmodel <- knn(tele_train, tele_test, tele_train_labels, k = 100)
```

## KNN Model Testing
```{r}
confusionMatrix(as.factor(KNNmodel), as.factor(tele_test_labels), positive = "1")

#Kappa for this model = 0.1989
```


## ANN Model Creation
```{r, cache= TRUE}
# install.packages('neuralnet')
library(neuralnet)
model_ann <- neuralnet(yyes ~ ., data = tele_train_full, hidden = 1)
plot(model_ann)
```

## ANN Model Testing
```{r, cache= TRUE}
library (caret)
ann_pred <- predict(model_ann, tele_test_full)
predbin_ann <- ifelse(ann_pred >= 0.5, 1, 0)
confusionMatrix(as.factor(predbin_ann), as.factor(tele_test_full$yyes), positive = "1")

#Kappa for this model = 0.3072
```

## Decision Tree Model Creation
```{r}
library(C50)

teletree <- C5.0(as.factor(yyes) ~., data=tele_train_full)
```

## Decision Tree Model Testing
```{r}
tree_pred <- predict(teletree, tele_test_full)
confusionMatrix(as.factor(tree_pred), as.factor(tele_test_full$yyes), positive = "1")

#Kappa for this model is 0.3623
```


## Random Forest Model Creation
```{r}
library(randomForest)

forestmodel <- randomForest(as.factor(yyes) ~., data = tele_train_full)
```


## Random Forest Model
```{r}
forest_pred <- predict(forestmodel, tele_test_full)
forest_bin <- ifelse(forest_pred )
confusionMatrix(as.factor(forest_pred), as.factor(tele_test_full$yyes), positive = "1")

#Kappa for this model is 0.3124
```


# Combining Our Models

## Adding Prediction Columns for Every Model
```{r}
#tele_test_full$LogPred <- predbin_log
#tele_test_full$KNNPred <- KNNmodel
#tele_test_full$KNNPred <- ifelse(tele_test_full$KNNPred == "1", 1, 0)
#tele_test_full$ANNPred <- predbin_ann

telestack <- data.frame(tele_test_full$yyes, predbin_log, KNNmodel, predbin_ann, tree_pred, forest_pred)

summary(telestack)
```

## Averaging the Predictions
```{r}
tele_test_full$FinalPred <- ifelse((
    (tele_test_full$LogPred + tele_test_full$KNNPred + tele_test_full$ANNPred) / 3) >= 0.6, 1, 0)

confusionMatrix(as.factor(tele_test_full$FinalPred), as.factor(tele_test_full$yyes), positive = "1")
```

## Final Profit from Our Combined Model
```{r}
Profit <- 
Profit
```


